---
title: "PREHAB study, bc cohort"
author: "Elke van Daal"
date: "2023-10-09"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This subgroup analysis will investigate the effect of a multimodal prehabilitation program on functional status outcomes in patients undergoing an autologous breast reconstruction, compared to standard preoperative care. Moreover, it will be investigated whether multimodal prehabilitation has an effect on the occurence of postoperative complications.

## Load packages
```{r packages and data, include = FALSE}
library(tidyverse)
library(naniar)
library(tableone)
library(flextable)
library(sjPlot)
library(readxl)
library(hablar)
library(performance)
library(skimr)
library(gt)

source("C:/Users/Elke van Daal/Documents/Radboud UMC/Fit4Society/File for codebook use as source 8-5.R")
sf_36 <- read.csv("C:\\Users\\Elke van Daal\\Documents\\R\\Fit4Society\\F4S_PREHAB_trial_SF36_JUIST_-_Nederlands_export_20231009.csv",
                  sep = ';')
```


```{r data cleaning, include = FALSE}

# Filter data for cluster BC
full_data_bc  <- full_data %>% filter(surgery_type == 'Breast')

# Delete useluss columns
bc_data <- full_data_bc %>% select(-id_status, -site, -incl_16, -surgery, -incl_ic, -incl_ic_version,
                   -contains('testroom'), -version_ic_2, -(254:262), -contains('date'),
                   -contains('dist'), -contains('reactance'), -contains('resistance'),
                   -contains('ffm'),
                   -contains('_fh'), -contains('hkk_stand'), -contains('hkk_side'),
                   -contains('pgsga1'), -contains('pgsga2'), -contains('pgsga3'), - contains('pgsga4'),
                   -contains('cycling_test'),
                   -contains('ar_hf'), -contains('ar_w'), -contains('sr_w'), -contains('sr_hf'),
                   -contains('1rm_stand'), -contains('1rm_w'), -contains('1rm_r'),
                   -scr_hb, -scr_gluc, -scr_acsm, -fysio_ref, -contains('_g8'),
                   -scr_ger, -surgery_gyn, -f4s_car, -f4s_long, -f4s_ger,
                   -no_training_reason, -no_training_reason_expl, -neoadjuvant_therapy,
                   -asa_score, -hemoglobin_preoperative_anesthesiology, -hemoglobin_preoperative,
                   -final_measurement_loc, -contains('supp'), -contains('complication'),
                   -surgery_technique, -surgery_procedure, different_surgery, -different_surgery_text,
                   -mortality_30_days, -adjuvant_therapy,
                   -contains('intention'), -contains('appoint'), -proms_mm4_mm5)

# Check completion rate bc data
bc_data <- bc_data %>%
  arrange(id) %>%
  mutate(m1_completed = case_when(
    m1_length > 1 ~ 1,
    is.na(m1_length) ~ 0
  ),
  m2_completed = case_when(
    m2_length > 1 ~ 1,
    is.na(m2_length) ~ 0
  ),
  m3_completed = case_when(
    m3_length > 1 ~ 1,
    is.na(m3_length) ~ 0
  ))
# Change name of ID variable
sf_36 <- sf_36 %>%
  rename(id = Castor.Participant.ID) %>%
  mutate(id = as.integer(str_remove(id, 'F4S_')))

# Semi join with bc_data to keep participants from ABR cluster
sf36_bc <- semi_join(sf_36, bc_data, by = 'id')
sf36_bc <- sf36_bc %>% arrange(id) %>%
  mutate(survey_completed = case_when(
    Survey.Progress > 99 ~ 1,
    Survey.Progress < 100 ~ 0
  ))


```

## Completion rate PREHAB trial
Completion rates of measurement 1, 2 and 3 (in testroom) for full cohort, and seperated for intervention/control.

```{r completion rates testroom, echo = FALSE}
bc_data %>%
  summarise(m1_completion_rate = mean(m1_completed),
         m2_completion_rate = mean(m2_completed),
         m3_completion_rate = mean(m3_completed),
         count = n())

bc_data %>%
  filter(group == 'Intervention') %>%
    summarise(m1_completion_rate = mean(m1_completed),
         m2_completion_rate = mean(m2_completed),
         m3_completion_rate = mean(m3_completed),
         count = n())

bc_data %>%
  filter(group == 'Control') %>%
    summarise(m1_completion_rate = mean(m1_completed),
         m2_completion_rate = mean(m2_completed),
         m3_completion_rate = mean(m3_completed),
         count = n())

```

## Completion rate SF36
Demonstrate completion rate of SF36 at different measurement points (for full cohort, and seperated by intervention vs control)
```{r completion rates sf36, echo=FALSE}
# full cohort
sf36_bc %>%
  group_by(Survey.Package.Name) %>%
  summarise(mean_completion_rate = mean(survey_completed),
            count = n()) 
# full join
full_bc_sf36 <- full_join(sf36_bc, bc_data, by = 'id')

# intervention cohort
full_bc_sf36 %>% filter(group == 'Intervention') %>%
  group_by(Survey.Package.Name) %>%
  summarise(mean_completion_rate = mean(survey_completed),
            count = n()) 

# control cohort
full_bc_sf36 %>% filter(group == 'Control') %>%
  group_by(Survey.Package.Name) %>%
  summarise(mean_completion_rate = mean(survey_completed),
            count = n()) 
```


